---
title: <center><span style="color:SteelBlue">FDR</span></center>
output: html_document
---

```{r}
library(pcadapt)
source("~/Documents/thesis/git/FDR/fdrUtils.R")
geno <- as.matrix(read.table(system.file("extdata", "geno3pops.pcadapt", package = "pcadapt")))
gt <- 1:150
x <- pcadapt(geno, K = 2, method = "mahalanobis")
y <- pcadapt(geno, K = 2, method = "communality")
rank.stat.1 <- sort(x$pvalues, decreasing = FALSE, index.return = TRUE)$ix #any set of p-values
rank.stat.2 <- sort(y$pvalues, decreasing = FALSE, index.return = TRUE)$ix
```

The functions `compute.fdr` and `compute.power` defined below respectively compute the values of FDR and power for a list of candidates (`list`) and a given list of true positives (`ground.truth`).

```{r}
compute.fdr = function(list, ground.truth){
  if (length(list) == 0){
    x <- 0
  } else {
    x <- sum(!(list %in% ground.truth)) / length(list)
  }
  return(x)
}

compute.power = function(list, ground.truth){
  if (length(ground.truth) == 0){
    warning("The list of true positives is empty.")
  } else {
    x <- sum(list %in% ground.truth) / length(ground.truth)
  }
  return(x)
}
```

Now if you want to plot the power as a function of the false discovery rate, you need to compute both power and FDR for any list of candidates which length should ideally vary from one to the total number of markers. What you want to do is ranking your markers according to their p-value, then compute both FDR and power for the marker with the lowest p-value, store both values in a data frame, then add the second marker with the lowest p-value, compute both FDR and power, store them in the data frame, and so on. The function below takes on these computations.

```{r}
create.fdr.pow = function(list, ground.truth, lmax = length(list), smooth = TRUE){
  fdr <- 0
  pow <- 0
  s <- seq(1, lmax, by = 1)
  for (k in s){
    l <- list[1:k]
    fdr <- c(fdr, compute.fdr(l, ground.truth))
    pow <- c(pow, compute.power(l, ground.truth))
  }
  res <- NULL
  idx <- sort(fdr, decreasing = FALSE, index.return = TRUE)$ix
  fdr <- fdr[idx]
  pow <- pow[idx]
  if (smooth == FALSE){
    res$fdr <- fdr
    res$pow <- pow
  } else if (smooth == TRUE){
    pow.old <- 0
    fdr.old <- 0
    aux.fdr <- 0
    aux.pow <- 0
    for (val in 1:length(fdr)){
      if (pow[val] >= pow.old){
        aux.fdr <- c(aux.fdr, fdr[val])
        aux.pow <- c(aux.pow, pow[val])
        pow.old <- pow[val]
      }
    }
    res$fdr <- aux.fdr
    res$pow <- aux.pow
  }
  return(res)
}
```

Now all we need is a function to generate a data frame so we can visualize the result with `ggplot2`.

```{r}
# Generate fdr and power values for each method:
res.1 <- create.fdr.pow(rank.stat.1, gt, smooth = TRUE)
df.1 <- create.df(res.1, "Mahalanobis")
res.2 <- create.fdr.pow(rank.stat.2, gt, smooth = TRUE)
df.2 <- create.df(res.2, "Communality")

df <- rbind(df.1, df.2)
colnames(df) <- c("Software", "FDR", "Power")
df[, 1] <- as.character(df[, 1])
df[, 2] <- as.numeric(as.character(df[, 2]))
df[, 3] <- as.numeric(as.character(df[, 3]))
```

```{r, fig.width = 7, fig.height = 5, fig.align = 'center'}
require(ggplot2)
p0 <- ggplot(data = df, aes(x = FDR, y = Power)) + 
  geom_line(aes(color = Software), size = 2, na.rm = TRUE) +
  xlim(0, 1) + ylim(0, 1) +
  theme_bw() +
  theme(axis.text = element_text(size = 15),
        axis.title = element_text(size = 15, face = "bold"),
        title = element_text(size = 15, face = "bold"),
        legend.text = element_text(size = 15),
        legend.key.height = unit(1, "line"),
        legend.key.width = unit(3, "line")
  )
print(p0)
```

